---
title: "My R Markdown"
author: "David Sanchez"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

R Markdown is a way to write documents that combine regular text, R code, and math in one file. When you knit the file, R runs the code, inserts the results, and outputs a clean report. This means the analysis and the explanation stay together, which makes it easier to update your work later without copying and pasting results.

# What Is R Markdown?

R Markdown uses a simple syntax for formatting. Headings are created with `#`, lists use `-` or `*`, and you can make text *italic* or **bold** with a few characters. Instead of clicking buttons like in Word, you type the formatting directly into the document. The nice part is that the same `.Rmd` file can be turned into HTML, PDF, or Word just by changing the output options and knitting again.

# Narrative Text and Structure

In a typical R Markdown report, I can explain what I am doing in plain language, then show the code and output right below that explanation. For example, I might describe a dataset, run a summary, and then talk about what the numbers mean. This feels more organized than having code in one place and a separate write-up somewhere else. It also helps keep a record of the steps I took so I can remember my process in the future.

# Math with LaTeX

R Markdown also supports LaTeX math, which is useful when I need to write formulas or show a little bit of notation.

I can use inline math inside a sentence, like this: $ \alpha + \beta = \gamma $.

I can also write a displayed equation on its own line. For example, the quadratic formula can be written as:

$$
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$

Having math built into the document is helpful when I need to explain models, statistics, or any calculations more clearly.

# Data and Code Chunks

Next, I can add R code chunks. These chunks are executed when the document is knit, and the results appear right under the code.

## Loading a Dataset and Running a Summary

```{r data-summary}
# Use a built-in data set called 'mtcars'
data(mtcars)

# Look at basic summary information for miles per gallon
summary(mtcars$mpg)

# Calculate the mean miles per gallon
mean(mtcars$mpg)

